\thispagestyle{empty}
\begin{center}
\fbox{
\parbox{13cm}{
Copyright (C) 2020-2022 mactonya @ \href{https://github.com/mactonya/}{https://github.com/mactonya/}. \\
Permission is granted to copy,
distribute and/or modify this document
under the terms of the GNU Free Documentation License,
Version 1.3 or any later version published by the Free Software Foundation; 
with the Invariant Sections being Prologue.
A copy of the license is included in the section entitled "GNU
Free Documentatin License".
}}

\vspace{48pt}
\emph{Special thanks to the following contributers:}
\end{center}
    
\newpage

\chapter{Prologue}
Over a few months I want to improve my skills in solving algebra problems. I tried to find a textbook that can serves me good and is good enough to use in self-study. 

Eventually, this is what I felt the most ``comfortable'' book in my opinion. It doesn't contain that much unlike Dummit \& Foote, but the writing style, the explanation, and the exercises really served me well.

So here is the solution to Algebra : Chapter 0. There are a few important points to note here:
\begin{itemize}
	\item The solution is \emph{only} hosted on my GitHub page 
	\begin{center}
		\href{https://github.com/mactonya/algebra-chapter-0-solutions}{https://github.com/mactonya/algebra-chapter-0-solutions}.
	\end{center} 
	If you find this document outside this page, you might have an outdated version of the solution which might have errors, so please be aware.
    \item I will update the solution irregularly.
    \item I'll try to write this beginner-friendly (as I am also a beginner), so the answer might be way too detailed/verbose. Sorry if you find this annoying. 
    \item If you found an error in the solutions, typos, bad grammar or want to give an advise on LaTeX formatting, etc., don't hesitate to open an issue or a pull request on my repo. 
    \item \textbf{PRs to new solutions are now open.} You are free to write solutions for this document now. When writing a solution, be sure to make it very beginner friendly: you should make all logics, the use of theorems and the idea very clear. You are also very welcome to refine the proofs if they are unclear.

\end{itemize}

Best,

\begin{flushright}
mactonya @ \href{https://github.com/mactonya/}{https://github.com/mactonya/} \\
Department of Mathematics, National Taiwan University \\
Updated December 29th, 2021
\end{flushright}
